Experiment 3: Replication Analysis

### 2024-08-21 group-a/E1-analysis-comparison-to-Hartshorne.Rmd
E2 and E3 materials sections, calibration plots

jh_E1_spag_fig <- ggplot(jh.cumulative.fixation.data.summary.min, aes(x=t.window, y=cumulative.fixation.m, fill=object_class, shape=verb_type, group=interaction(verb_type, object_class)))+
  geom_line()+
  geom_point(aes(fill = object_class), size=2, color = "black")+ 
  scale_fill_manual(name = "Object Type",values=c(distractor = "white", target.object = "black"), labels = c("distractor", "target"))+
  scale_shape_manual(values=c(22,21))+
  guides(fill = guide_legend(override.aes=list(shape=21))) +
  theme_bw()+
  scale_y_continuous(limits=c(0,1))+
  scale_x_continuous(expand=c(0.01,0.01))+
  labs(x="Time from Verb Onset (ms)", y="Probability", shape="Verb Type", fill="Object Type")+
  geom_vline(xintercept = mean(jh.word.dur.avg$Total)) +
  theme(panel.grid=element_blank(), legend.position = "none")+
  ggtitle('In-lab sample')

>>>>

jh_E1_spag_fig <- ggplot(jh.cumulative.fixation.data.summary.min, aes(x=t.window, y=cumulative.fixation.m, fill=object_class, shape=verb_type, group=interaction(verb_type, object_class)))+
  geom_line()+
  geom_point(aes(fill = object_class), size=2, color = "black")+ 
  scale_fill_manual(name = "Object Type",values=c(distractor = "white", target.object = "black"), labels = c("distractor", "target"))+
  scale_shape_manual(values=c(22,21))+
  guides(fill = guide_legend(override.aes=list(shape=21))) +
  theme_bw()+
  scale_y_continuous(limits=c(0,1))+
  scale_x_continuous(expand=c(0.01,0.01))+
  labs(x="Time from Verb Onset (ms)", y="Probability", shape="Verb Type", fill="Object Type")+
  geom_vline(xintercept = mean(jh.word.dur.avg$Total)) +
  theme(panel.grid.minor=element_blank(), legend.position = "none")+
  ggtitle('In-lab sample')

### 2024-08-21 group-a/E1-analysis-replication.Rmd
E2 and E3 materials sections, calibration plots

```{r summarize calibration data, eval=F}
#printed?
validation.accuracy.data %>% 
  group_by(subject_id) %>%
  count() %>%
  group_by(n) %>%
  count()
```

@@

```{r plot subjects by validation, eval=F}
#printed?
ggplot(validation.percent, aes(x=subject_id, y=M, ymax = MAX, ymin=MIN))+
  geom_pointrange() +
  theme_classic()
```
<!-- Set criteria for minimal exclusions (aggressive is later) -->

@@

E1_spag_fig_remote <- ggplot(cumulative.fixation.data.summary.min, aes(x=t.window, y=cumulative.fixation.m, fill= object_class, shape=verb_type))+
  geom_line()+
  geom_point(aes(fill = object_class), size=2, color = "black")+ 
  scale_fill_manual(name = "Object Type",values=c(distractor = "white", target.object = "black"), labels = c("distractor", "target"))+
  scale_shape_manual(name = "Verb Type", values=c(22,21))+
  guides(fill = guide_legend(override.aes=list(shape=21))) + #Woo-hoo! Add this line to fix the legend
  labs(x="Time from Verb Onset (ms)", y="Probability", fill = "object type")+
  theme_bw()+
  scale_y_continuous(limits=c(0,1))+
  scale_x_continuous(expand=c(0.01,0.01))+
  geom_vline(xintercept = mean(word.dur.avg$Total)) +
  theme(panel.grid=element_blank(), axis.title.x = element_blank())+
  ggtitle('Remote sample')

@@

```{r Model 1 effect size by calibration}
#merge with validation percent

@@

```{r E1-calib-effect, fig.cap='Calibration scores plotted against target advantage scores (cumulative proportion of fixations to the target minus cumulative proportion of fixations to competitors) at the end of the pre-noun time window.'}
#The one corr that came out: noun window, restricting condition only
ggplot(cali.analy.1, aes(x=M, y=restricting))+
  geom_point()+
  geom_smooth(method="lm", formula = y ~ x)+
  labs(x="Calibration Score", y="Target Advantage Score")

>>>>

```{r summarize calibration data, eval=F}
validation.accuracy.data %>% 
  group_by(subject_id) %>%
  count() %>%
  group_by(n) %>%
  count()
```

@@

```{r plot subjects by validation, eval=F}
ggplot(validation.percent, aes(x=subject_id, y=M, ymax = MAX, ymin=MIN))+
  geom_pointrange() +
  theme_classic()
```
<!-- Set criteria for minimal exclusions (aggressive is later) -->

@@

E1_spag_fig_remote <- ggplot(cumulative.fixation.data.summary.min, aes(x=t.window, y=cumulative.fixation.m, fill= object_class, shape=verb_type))+
  geom_line()+
  geom_point(aes(fill = object_class), size=2, color = "black")+ 
  scale_fill_manual(name = "Object Type",values=c(distractor = "white", target.object = "black"), labels = c("distractor", "target"))+
  scale_shape_manual(name = "Verb Type", values=c(22,21))+
  guides(fill = guide_legend(override.aes=list(shape=21))) + #Woo-hoo! Add this line to fix the legend
  labs(x="Time from Verb Onset (ms)", y="Probability", fill = "object type")+
  theme_bw()+
  scale_y_continuous(limits=c(0,1))+
  scale_x_continuous(expand=c(0.01,0.01))+
  geom_vline(xintercept = mean(word.dur.avg$Total)) +
  theme(panel.grid.minor=element_blank(), axis.title.x = element_blank())+
  ggtitle('Remote sample')

@@

<!--CALIBRATION ANALYSIS-->
```{r Model 1 effect size by calibration}
#merge with validation percent

@@

```{r E1-calib-effect, fig.cap='Calibration scores plotted against target advantage scores (cumulative proportion of fixations to the target minus cumulative proportion of fixations to competitors) at the end of the pre-noun time window.'}
#The one corr that came out: noun window, restricting condition only
ggplot(cali.analy.1, aes(x=M, y=restricting))+
  geom_point()+
  geom_smooth(method="lm", formula = y ~ x)+
  labs(x="Calibration Score", y="Target Advantage Score")+
  theme_bw()+
  theme(panel.grid.minor = element_blank())

### 2024-08-21 group-b/E2-analysis-calibration.Rmd
E2 and E3 materials sections, calibration plots

```{r, eval = F}
ggplot(eyetracking.effects.by.subj, aes(x = mean_percent_in_roi, y = crit_bias))+
  geom_point()+
  geom_smooth(method = "lm")
```
```{r}

@@

Participants' calibration quality, measured as the mean percentage of fixations that landed within 200 pixels of the calibration point, varied substantially (between `r range(calib.by.subj$mean_percent_in_roi) %>% round(digits = 2)` %). 
The quality of a participant's calibration was not significantly correlated with the participant's effect size ( _Pearson's r_= `r m_calib_r`, _p_ = `r m_calib_p`) as measured by the difference between the proportion of looks to the critical quadrant minues the average proportion of looks to the average of the other three quadrants.

>>>>

```{r E2-calib-effect, fig.cap = 'Calibration scores plotted against gaze bias (the difference between the proportion of looks to the critical quadrant minus the average proportion of looks to the average of the other three quadrants).'}
ggplot(eyetracking.effects.by.subj, aes(x = mean_percent_in_roi, y = crit_bias))+
  geom_point()+
  geom_smooth(method = "lm", formula = y ~ x) +
  labs(x="Calibration Score", y="Gaze Bias")+
  theme_bw()+
  theme(panel.grid.minor = element_blank())
```

@@

Participants' calibration quality, measured as the mean percentage of fixations that landed within 200 pixels of the calibration point, varied substantially (between `r range(calib.by.subj$mean_percent_in_roi) %>% round(digits = 2)` %). 
The quality of a participant's calibration was not significantly correlated with the participant's effect size ( _Pearson's r_= `r m_calib_r`, _p_ = `r m_calib_p`) as measured by the difference between the proportion of looks to the critical quadrant minus the average proportion of looks to the average of the other three quadrants (see Figure\ \@ref(fig:E2-calib-effect))

### 2024-08-21 group-b/E2-analysis-replication.Rmd
E2 and E3 materials sections, calibration plots

### Replication
<!--Summarize proportion of views in each quadrant for each trial-->
```{r}
free.view.summary.trial.data <- free.view.data %>%
  group_by(subject_id, trial_index, relation) %>%
  summarize(critical = sum(normalized_quadrant == 'critical')/n(),
            first = sum(normalized_quadrant == 'first')/n(),
            second = sum(normalized_quadrant == 'second')/n(),
            third = sum(normalized_quadrant == 'third')/n()) %>%
  pivot_longer(c("critical", "first", "second", "third"), names_to = "normalized_quadrant", values_to = "proportion")
```
<!--Summarize by subject-->
```{r}
free.view.summary.subject.data <- free.view.summary.trial.data %>%
  group_by(subject_id,relation,normalized_quadrant) %>%
  summarize(proportion = mean(proportion))
```

@@

__Eye-gaze__. Looks during the retrieval period were categorized as belonging to one of four quadrants based on the x,y coordinates. The critical quadrant was the one in which the to-be-retrieved object had been previously located during encoding. The other three quadrants were semi-randomly labeled "first", "second," third" (e.g., when the critical quadrant was in the top left, the "first" quadrant was the top right quadrant, but when the critical quadrant was in the top right, "first" corresponded to bottom right, etc.). In both the fixed- and free-viewing condition, participants directed a larger proportion of looks to the critical quadrant (see Figure \@ref(fig:E2-gaze-fig-both-conds)). This bias appeared larger in the free-viewing condition, suggesting that the manipulation was (somewhat) effective.

@@

__Response Time and Accuracy__. Participants' response times and accuracies on memory questions are summarized in Figure \@ref(fig:E2-rt-acc-fig). 
Both dependent variables were analyzed with linear mixed-effects model with relation type (interobject = -0.5, intraobject=0.5) and viewing_condition (fixed = -0.5, free=0.5) and their interaction as the predictors. 
The model included random intercepts for participants^[ `lme4` syntax: `lmer(DV ~ relation_type*viewing_condition + (1|subject_id))`]. 
Accuracy did not differ significantly between interobject and intraobject questions (_b_ =  `r E2_acc_model_rel %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_acc_model_rel %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E2_acc_model_rel %>% pull(p.value) %>% round(digits = 2)`). Participants were less accurate in the free viewing condition than the fixed condition (_b_ =  `r E2_acc_model_cond %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_acc_model_cond %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E2_acc_model_cond %>% pull(p.value) %>% round(digits = 2)`). 
Response times were slower for interobject (e.g., "The train is to the right of the taxi.") than intraobject (e.g., "The train is facing right.") questions (_b_ =  `r E2_RT_model_rel %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_RT_model_rel %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001). Response times were slower in the free viewing condition than the fixed condition (_b_ =  `r E2_RT_model_cond %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_RT_model_cond %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001). 
The interaction was not a significant predictor for response times or accuracy.
These behavioral results are inconsistent with the original findings.

@@

One possibility is that in-lab participants were much more compliant with the instruction to keep their gaze on central fixation (though these data are not reported in the original paper). When  analyzing results from the subset of participants (N = `r length(successful_fixed)`) who were most compliant during the fixed-viewing block (at least 25% of their looks fell within 20% of the center of the display), the viewing condition effects and the interactions were not signficant. Given the smaller sample size we do not interpret these results further.

>>>>

<!--Summarize proportion of views in each quadrant for each trial-->
```{r}
free.view.summary.trial.data <- free.view.data %>%
  group_by(subject_id, trial_index, relation) %>%
  summarize(critical = sum(normalized_quadrant == 'critical')/n(),
            first = sum(normalized_quadrant == 'first')/n(),
            second = sum(normalized_quadrant == 'second')/n(),
            third = sum(normalized_quadrant == 'third')/n()) %>%
  pivot_longer(c("critical", "first", "second", "third"), names_to = "normalized_quadrant", values_to = "proportion")
```
<!--Summarize by subject-->
```{r}
free.view.summary.subject.data <- free.view.summary.trial.data %>%
  group_by(subject_id,relation,normalized_quadrant) %>%
  summarize(proportion = mean(proportion))
```

@@

### Eye-gaze
Looks during the retrieval period were categorized as belonging to one of four quadrants based on the x,y coordinates. The critical quadrant was the one in which the to-be-retrieved object had been previously located during encoding. The other three quadrants were labeled "first", "second," and "third" depending upon the location of the critical quadrant (e.g., when the critical quadrant was in the top left, the "first" quadrant was the top right quadrant, but when the critical quadrant was in the top right, "first" corresponded to bottom right, etc.). In both the fixed- and free-viewing condition, participants directed a larger proportion of looks to the critical quadrant (see Figure \@ref(fig:E2-gaze-fig-both-conds)). This bias appeared larger in the free-viewing condition, suggesting that the manipulation was somewhat effective.

@@

### Response Time and Accuracy
Participants' response times and accuracies on memory questions are summarized in Figure \@ref(fig:E2-rt-acc-fig). 
Both dependent variables were analyzed with linear mixed-effects model with relation type (interobject = -0.5, intraobject=0.5) and viewing_condition (fixed = -0.5, free=0.5) and their interaction as the predictors. 
The model included random intercepts for participants^[ `lme4` syntax: `lmer(DV ~ relation_type*viewing_condition + (1|subject_id))`]. 
Accuracy did not differ significantly between interobject and intraobject questions (_b_ =  `r E2_acc_model_rel %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_acc_model_rel %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E2_acc_model_rel %>% pull(p.value) %>% round(digits = 2)`). Participants were less accurate in the free viewing condition than the fixed condition (_b_ =  `r E2_acc_model_cond %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_acc_model_cond %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E2_acc_model_cond %>% pull(p.value) %>% round(digits = 2)`). 
Response times were slower for interobject (e.g., "The train is to the right of the taxi.") than intraobject (e.g., "The train is facing right.") questions (_b_ =  `r E2_RT_model_rel %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_RT_model_rel %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001). Response times were slower in the free viewing condition than the fixed condition (_b_ =  `r E2_RT_model_cond %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_RT_model_cond %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001). 
The interaction was not a significant predictor for response times or accuracy.
These behavioral results are inconsistent with the original findings.

@@

One possibility is that the in-lab participants in @johanssonLookHereEye2014 were much more compliant with the instruction to keep their gaze on central fixation (though these data are not reported in the original paper). When  analyzing results from the subset of participants (N = `r length(successful_fixed)`) who were most compliant during the fixed-viewing block (at least 25% of their looks fell within 20% of the center of the display), the viewing condition effects and the interactions were not signficant. Given the smaller sample size we do not interpret these results further.

### 2024-08-21 group-c/E3-analysis-calibration.Rmd
E2 and E3 materials sections, calibration plots

```{r E3-cal Plot Calibration Accuracy, echo=FALSE}
ggplot(subject.calibration.score, aes(x=mean_percent_in_roi))+
  stat_bin(binwidth = 10)+
  labs(x="Calibration Accuracy\n(% of samples within 200px of calibration point)")+
  theme_minimal()+
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        axis.title.y = element_blank())
```

@@

Calibration scores were not correlated with looking scores, regardless of which method was used to calculate looking scores.

```{r E3-cal Plot looking score (halves) by calibration, echo=FALSE}
ggplot(merged.eyetracking, aes(x=mean_percent_in_roi, y=looking.score.M.half))+
  geom_point()+
  geom_smooth(method="lm", formula = y ~ x)+
  labs(x="Calibration Score", y="Looking Score (Halves)")
```

```{r E3-cal Plot looking score (roi) by calibration, echo=FALSE, warning=FALSE}
ggplot(merged.eyetracking, aes(x=mean_percent_in_roi, y=looking.score.M.roi))+
  geom_point()+
  geom_smooth(method="lm", formula = y ~ x)+
  labs(x="Calibration Score", y="Looking Score (ROIs)")
```

@@

We then looked at the correlation of calibration scores with the correlation between day 2 memory performance and day 1 looking scores for both kinds of behavioral and looking measures. None of the four relationships showed a significant correlation.

```{r E3-cal Plot correlations with calibration score, echo=FALSE, warning=FALSE}
ggplot(looking.correlations.subjects.tidy, aes(x=mean_percent_in_roi, y=z))+
  geom_point()+
  geom_smooth(method="lm", formula=y~x)+
  facet_grid(behavioral_measure ~ looking_measure)

>>>>

```{r E3-cal Plot Calibration Accuracy, echo=FALSE, eval=FALSE}
#This figure isn't referred to in the body of the text, and we have the scatterplots, so I'm cutting this for now
ggplot(subject.calibration.score, aes(x=mean_percent_in_roi))+
  stat_bin(binwidth = 10)+
  labs(x="Calibration Accuracy\n(% of samples within 200px of calibration point)")+
  theme_minimal()+
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        axis.title.y = element_blank())
```

@@

Calibration scores were not correlated with looking scores, regardless of whether scores were computed using the halves coding method (see Figure \ \@ref(fig:E3-cal-Plot-looking-score-(halves)-by-calibration) or the ROI coding method (see  Figure \ \@ref(fig:E3-cal-Plot-looking-score-(roi)-by-calibration)).

```{r E3-cal-Plot-looking-score-(halves)-by-calibration, echo=FALSE, warning=FALSE, fig.cap = 'Calibration scores plotted against looking scores using the left-vs.-right halves coding method (proportion of gaze samples to the half of the screen containing the new image out of all gaze samples).'}
ggplot(merged.eyetracking, aes(x=mean_percent_in_roi, y=looking.score.M.half))+
  geom_point()+
  geom_smooth(method="lm", formula = y ~ x)+
  labs(x="Calibration Score", y="Looking Score (Halves)")+
  theme_bw()+
  theme(panel.grid.minor = element_blank())

```{r E3-cal-Plot-looking-score-(roi)-by-calibration, echo=FALSE, warning=FALSE, fig.cap = 'Calibration scores plotted against looking scores using the ROI coding method (proportion of gaze samples to the new image out of all gaze samples).'}
ggplot(merged.eyetracking, aes(x=mean_percent_in_roi, y=looking.score.M.roi))+
  geom_point()+
  geom_smooth(method="lm", formula = y ~ x)+
  labs(x="Calibration Score", y="Looking Score (ROIs)") +
  theme_bw()+
  theme(panel.grid.minor = element_blank())

@@

We then looked at the correlation of calibration scores with the correlation between day 2 memory performance and day 1 looking scores for both kinds of behavioral and looking measures. None of the four relationships showed a significant correlation (see Figure\ \@ref(fig:E3-cal-Plot-correlations-with-calibration-score)).

```{r E3-cal-Plot-correlations-with-calibration-score, echo=FALSE, warning=FALSE, fig.cap='The relation between calibration scores and experimental effect size, defined as the correlation between Day 1 looking scores and Day 2 memory performance. Looking scores were either coded using the halves method (left panels) or ROI method (right panels); memory performance was measured using confidence ratings (top panels) or reaction time for correct recognition judgments (bottom panels).}
# Set up facet label names for behavioral_measure variable
behav.labs <- c("Confidence", "Reaction Time")
names(behav.labs) <- c("confidence", "rt")

# Set up facet label names for looking_measure variable
look.labs <- c("Halves Method", "ROI Method")
names(look.labs) <- c("half", "roi")

ggplot(looking.correlations.subjects.tidy, aes(x=mean_percent_in_roi, y=z))+
  geom_point()+
  geom_smooth(method="lm", formula=y~x)+
  facet_grid(behavioral_measure ~ looking_measure,
             labeller = labeller(behavioral_measure = behav.labs, looking_measure =
                                   look.labs))+
  labs(x="Calibration Score", y="Correlation (Looking Score, Memory)") +
  theme_bw()+
  theme(panel.grid.minor = element_blank())
```

### 2024-08-21 group-c/E3-analysis-replication.Rmd
E2 and E3 materials sections, calibration plots

The mean looking score was `r mean(t.test.data1$M.looking.score)` (*SD* = `r sd(t.test.data1$M.looking.score)`). This significantly greater than 0.5, *t*(`r t.test.day1$parameter`) = `r t.test.day1$statistic`, *p* = `r t.test.day1$p.value`, indicating that participants did show a preference for looking at the novel objects.

@@

```{r plot-cumulative-looking-score, echo=FALSE, fig.cap="Cumulative looking score over the 5 second exposure during part 2 of day 1. Error bars represent +/- 1 SEM."}
ggplot(day.1.looking.by.time.summary, aes(x=t, y=M, ymin=M-SE, ymax=M+SE))+
  geom_pointrange()+
  labs(x = "Time (ms)", y = "Cumulative Looking Score")+
  theme_bw()+
  theme(panel.grid.minor = element_blank())
```

@@

Participants correctly identified whether the image was familiar or unfamiliar `r mean(day2.accuracy$accuracy)*100`% (*SD* = `r sd(day2.accuracy$accuracy*100)`) of the time. After excluding the `r length(subjects.100.percent.accurate)` participants who responded correctly to all images, the average confidence rating for correct responses (M = `r confidence.test.data.filtered %>% filter(correct_recognition == TRUE) %>% pull(M.confidence) %>% mean()`; SD = `r confidence.test.data.filtered %>% filter(correct_recognition == TRUE) %>% pull(M.confidence) %>% sd()`) was significantly higher than their average confidence ratings for incorrect responses (M = `r confidence.test.data.filtered %>% filter(correct_recognition == FALSE) %>% pull(M.confidence) %>% mean()`; SD = `r confidence.test.data.filtered %>% filter(correct_recognition == FALSE) %>% pull(M.confidence) %>% sd()`), t(`r confidence.t.test$parameter`) = `r confidence.t.test$statistic`, p = `r confidence.t.test$p.value` . Among the same subset of participants, response times for correct responses (M = `r rt.test.data.filtered %>% filter(correct_recognition == TRUE) %>% pull(M.rt) %>% mean()`, SD = `r rt.test.data.filtered %>% filter(correct_recognition == TRUE) %>% pull(M.rt) %>% sd()`) were also significantly faster than for incorrect responses (M = `r rt.test.data.filtered %>% filter(correct_recognition == FALSE) %>% pull(M.rt) %>% mean()`, SD = `r rt.test.data.filtered %>% filter(correct_recognition == FALSE) %>% pull(M.rt) %>% sd()`), t(`r rt.t.test$parameter`) = `r rt.t.test$statistic` , p = `r rt.t.test$p.value`.

@@

To see whether preferentially looking an the unfamiliar object on day 1 was correlated with confidence and response time for correct responses on day 2, we computed the correlation coefficient between day 1 looking scores and day 2 confidence/RT for each participant. Following the original analysis, we transformed these values using the Fisher p-to-z transformation. Using one-sample t-tests, we found no significant different from 0 for the correlation between looking score and confidence ratings, t(`r looking.confidence.correlation.t.test$parameter`) = `r looking.confidence.correlation.t.test$statistic`, p = `r looking.confidence.correlation.t.test$p.value` (excluding the subjects who gave the same confidence judgment for all images), nor the the correlation between looking score and RT, t(`r  looking.rt.correlation.t.test$parameter`) = `r looking.rt.correlation.t.test$statistic`, p = `r looking.rt.correlation.t.test$p.value`.

```{r Plot Looking Score Correlations, echo=FALSE, warning=FALSE}
ggplot(looking.plus.behavioral %>% filter(rt_recognition < 10000), aes(x=looking.score, y=rt_recognition))+
  geom_point()+
  theme_bw()
```

>>>>

The mean looking score was `r mean(t.test.data1$M.looking.score)` (*SD* = `r sd(t.test.data1$M.looking.score)`). This was significantly greater than 0.5 (*t*(`r t.test.day1$parameter`) = `r t.test.day1$statistic`, *p* = `r t.test.day1$p.value`), indicating that participants did show a preference for looking at the novel objects.

@@

```{r plot-cumulative-looking-score, echo=FALSE, eval=FALSE, fig.cap="Cumulative looking score over the 5 second exposure during part 2 of day 1. Error bars represent +/- 1 SEM."}
#This (the fig and the DV) isn't referred to in the body of the text, so I'm cutting this for now
ggplot(day.1.looking.by.time.summary, aes(x=t, y=M, ymin=M-SE, ymax=M+SE))+
  geom_pointrange()+
  labs(x = "Time (ms)", y = "Cumulative Looking Score")+
  theme_bw()+
  theme(panel.grid.minor = element_blank())
```

@@

Participants correctly identified whether the image was familiar or unfamiliar `r mean(day2.accuracy$accuracy)*100`% (*SD* = `r sd(day2.accuracy$accuracy*100)`) of the time. After excluding the `r length(subjects.100.percent.accurate)` participants who responded correctly to all images, the average confidence rating for correct responses (M = `r confidence.test.data.filtered %>% filter(correct_recognition == TRUE) %>% pull(M.confidence) %>% mean()`; SD = `r confidence.test.data.filtered %>% filter(correct_recognition == TRUE) %>% pull(M.confidence) %>% sd()`) was significantly higher than their average confidence ratings for incorrect responses (M = `r confidence.test.data.filtered %>% filter(correct_recognition == FALSE) %>% pull(M.confidence) %>% mean()`; SD = `r confidence.test.data.filtered %>% filter(correct_recognition == FALSE) %>% pull(M.confidence) %>% sd()`), t(`r confidence.t.test$parameter`) = `r confidence.t.test$statistic`, p = `r confidence.t.test$p.value` . Among the same subset of participants, response times for correct responses (M = `r rt.test.data.filtered %>% filter(correct_recognition == TRUE) %>% pull(M.rt) %>% mean()`, SD = `r rt.test.data.filtered %>% filter(correct_recognition == TRUE) %>% pull(M.rt) %>% sd()`) were also significantly faster than for incorrect responses (M = `r rt.test.data.filtered %>% filter(correct_recognition == FALSE) %>% pull(M.rt) %>% mean()`, SD = `r rt.test.data.filtered %>% filter(correct_recognition == FALSE) %>% pull(M.rt) %>% sd()`), t(`r rt.t.test$parameter`) = `r rt.t.test$statistic` , p = `r rt.t.test$p.value`).

@@

To see whether preferentially looking an the unfamiliar object on day 1 was correlated with confidence and response time for correct responses on Day 2, we computed the correlation coefficient between Day 1 looking scores and Day 2 confidence/RT for each participant. Following the original analysis, we transformed these values using the Fisher p-to-z transformation. Using one-sample t-tests, we found no significant difference from 0 for the correlation between looking score and confidence ratings, t(`r looking.confidence.correlation.t.test$parameter`) = `r looking.confidence.correlation.t.test$statistic`, p = `r looking.confidence.correlation.t.test$p.value` (excluding the subjects who gave the same confidence judgment for all images), nor the the correlation between looking score and RT, t(`r  looking.rt.correlation.t.test$parameter`) = `r looking.rt.correlation.t.test$statistic`, p = `r looking.rt.correlation.t.test$p.value`.

```{r Plot Looking Score Correlations, echo=FALSE, warning=FALSE, eval=FALSE}
# #This isn't referred to in the text--it's between Figs 10 and 11

ggplot(looking.plus.behavioral %>% filter(rt_recognition < 10000), aes(x=looking.score, y=rt_recognition))+
  geom_point()+
  theme_bw()

```
